The fundamental shape of dynamic experiences is preserved in episodic memory

### 2018-07-09 main.tex
added methods up to list learning analyses

% \subsubsection{Matching recall events to video events}
% To figure out which video event each recall event referred to, we correlated the video events model and each recall events model. This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event.  To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.  The result was a list of video event indices for each participant. These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).

>>>>

\subsubsection{Matching recall events to video events}
To figure out which video event each recall event referred to, we correlated the video events model and each recall events model. This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event.  To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.  The result was a list of video event indices for each participant. These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).
